---
title: "Data Cleaning"
author: "Quinn Morris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyr")
install.packages("stringr")
install.packages("tibble")
```

# Library Imports
```{r}
library(stringr)
library(tibble)
library(dplyr)
```

# Gather Patient Filenames
This gets the file paths and the SIDS from the Data folder.
```{r}
data_folder <- "../Data/"
filenames <- list.files(data_folder, full.names=TRUE)
sid_files_full <- grep(pattern="[0-9]{4}_data\\.csv", filenames, value=TRUE)
sids <- as.integer(str_extract(sid_files_full, "[0-9]{4}"))
```

# EMM File Data Cleaning
This process aims to clean up the EMM Data file which contains all the response data relating to the patients.  
```{r}

# This file contains all the response data relating to the patients
EMM_data <- read.csv("../Data/EMEM_Alpha_Theta_n49_noBLC_tenths_Long_withMetadata_outliers.csv") 

# We will need to change a column name in the EMM Data from sendID too sentID
colnames(EMM_data)[which(names(EMM_data) == "sendID")]  <- "sentID"

# Remove X and X.1 columns from EMM Data. We use grepl to remove any columns starting with X
EMM_data <- EMM_data[,!grepl("^X",names(EMM_data))]

EMM_data <- select(EMM_data, sentID, sid, anyIU)
```

# Dataframe Join and Export
Here we cycle through the sid_files_full vector, import each file, co-register the data with the EMM_data folder, and export the newly made file to a separate folder. All the steps above can be skipped if these files are generated already.

```{r}
output_folder <- "../Data/co-registered files/"

for(pid in 1:length(sids)) {
  patient_dat <- read.csv(sid_files_full[pid]) # Read in the appropriate patient data based on the sid.
  x <- EMM_data %>% 
    filter(sid == sids[pid]) # Filter the columns based on the appropriate sid
  y <- aggregate(anyIU ~ sentID, data=x, FUN=mean) # Aggregate the anyIU per sentID. All we're looking for here is whether a person managed to generate an "idea unit" from the experience.
  
  out <- full_join(y, patient_dat, by="sentID") # I'll do a full join for now and export those. NA values will occur
  out <- add_column(out, sid=sids[pid], .before=1) # Add the sid as a column for identification and later merging.
  
  output_name <- paste(output_folder, paste(sids[pid], "_coregistered.csv", sep=""), sep="") # Format the names
  write.csv(out, output_name, row.names=TRUE)
}
```

# One Coregistered File
```{r} 
coregistered_filenames <- list.files(output_folder, full.names=TRUE)
coregistered_files_full <- grep(pattern="[0-9]{4}_coregistered\\.csv", filenames, value=TRUE)

df <- data.frame(matrix(ncol=length(names(out)), nrow=0))
colnames(df) <- names(out)

for(f in 1:length(coregistered_files_full)) {
  z <- read.csv(coregistered_filenames[f])
  df <- bind_rows(df, z)
}

output_name <- paste(output_folder, "cumulative_coregistered.csv", sep="")
write.csv(df, output_name, row.names=TRUE)
```