---
title: "Untitled"
author: "Quinn Morris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(FNN)
library(dplyr)
library(ggformula)

library(pROC)
library(FNN) # for comparison with KNN
library(caTools)

library(class)
library(caret)

library(car)
library(corrplot)

rm(list=ls())
```

# Data Loading
There's two ways to load in the data. The first is to load the files in via the cumulative co-registered data file. The other way is to load in all the labelled co-registered files themselves.
```{r}
data_dir <- "../Data/co-registered files/cumulative_coregistered.csv"
cumco_df <- read.csv(data_dir) 
cumco_df <- subset(cumco_df, select = -c(X, X.1, sentID))
```

## Data Subset Collection
This is a way to grab specific columns (and rows) from the cumco_df dataset based on patient id, electrode number, frequency value, and timestamp.
```{r}
library(schoolmath)

# This is a function that allows me to custom select columns based on their specific
# quality that pertains to story id (SID), electrode, hertz, and timestamp
get_cumco_subset <- function(dat, sid_=-1, e_=-1, hz_=-1, timestamp_=-1) {
  df <- dat
  
  # If we're filtering by sid
  if(sid_ != -1) {
    df <- df %>% filter(sid == sid_)
  }
  
  # Create logical vector for columns/variables to select
  selected_cols <- vector(length=dim(df)[2]) | TRUE # default is true
  
  # Selecting columns by electrode number
  if(e_ != -1) {
    e_num <- paste("e", as.integer(e_), "_", sep="")
    selected_cols <- selected_cols & grepl(e_num, colnames(df))
  }
  
  if(hz_ != -1) {
    hz_num <- "2Hz" # 2 by default
    if(is.decimal(hz_)) {
      hz_int <- floor(hz_)
      hz_dec <- floor((hz_int %% 1)*10)
      hz_num <- paste("_", hz_int, "pt", hz_dec, "Hz", sep="")
    }
    else {
      hz_num <- paste("_", hz_, "Hz", sep="")
    }
    
    # print(hz_num)
    selected_cols <- selected_cols & grepl(hz_num, colnames(df))
  }
    
  if(timestamp_ != -1) {
    # Grab column indexes that fulfill timestamp criteria
    t_num <- paste("s", timestamp_, "\\b", sep="")
    selected_cols <- selected_cols & grepl(t_num, colnames(df)) 
  }
  
  selected_cols[1:2] <- TRUE
  
  df <- df[, as.logical(selected_cols)]
  
  return(df)
}
```

### Grab subset of data by SID, Electrode, Hertz Value and/or Timestamp
```{r}
ex <- get_cumco_subset(cumco_df, sid_=1022, hz_=2, timestamp_=1)
ex$anyIU <- as.factor(ex$anyIU)
```

## Spread
```{r}
library(ggplot2)

ex_scaled <- scale(ex[-c(1,2)])
# ex_scaled <- ex[-c(1,2)]**2
ex_scaled <- cbind(ex[c(1,2)], ex_scaled)

for (col in 3:ncol(ex)) {
    hist <- hist(ex[,col], plot = FALSE)
    histScaled <- hist(ex_scaled[,col], plot = FALSE)

    plot(hist, col="lightblue", main=colnames(ex[col]), xlab="Hz")
    plot(histScaled, col="lightpink", add=TRUE)
}
```

# Model Selection and Creation
## PCA
```{r}
library(corrr)
library(ggcorrplot)
library(FactoMineR)
library(factoextra)

pca_threshold <- 0.9
```

### Checking for Varience and Collinearity
```{r}
corr_matrix <- cor(ex_scaled[,-c(1,2)]) 
corr_matrix
ggcorrplot(corr_matrix)

data.pca <- princomp(corr_matrix)
fviz_eig(data.pca, addLabels=TRUE)
# summary(data.pca)
# Calculate the index of the cumulative proportion of variance
get_num_vars_needed <- function(cum_pov_vec, threshold=0.9) {
  cum_prop <- 0.0
  index <- 1
  for(i in 1:length(cum_pov_vec)) {
    cum_prop <- cum_prop + cum_pov_vec[i]
    if(cum_prop <= threshold) {
      index <- i
    }
  }
  
  return(index+1)
}
cum_pov <- data.pca$sdev^2/sum(data.pca$sdev^2)
var_num <- get_num_vars_needed(cum_pov,pca_threshold)
```


### Retrying PCA
```{r}
# Reduce dimensionality
ex_pca <- ex_scaled[, 1:(var_num+2)] # Add +2 for sid and anyIU columns
corr_matrix <- cor(ex_pca[,-c(1,2)]) 
corr_matrix
ggcorrplot(corr_matrix)

data.pca <- princomp(corr_matrix)
fviz_eig(data.pca, addLabels=TRUE)
```


## KMeans
```{r}
scree_threshold <- 0.05
```

### WCSS Minimization
```{r}
set.seed(2023)

# Decide how many clusters to look at
n_clusters <- 20

# Initialize total within sum of squares error: wss
wss <- numeric(n_clusters)

# Look over 1 to n possible clusters
for (i in 1:n_clusters) {
  # Fit the model: km.out
  km.out <- kmeans(ex_pca[,-c(1,2)], centers = i, nstart = 20)
  # Save the within cluster sum of squares
  wss[i] <- km.out$tot.withinss
}

# Produce a scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

get_cluster_with_least_change <- function(wss_, threshold = 0.05) {
  index <- 1
  for(i in 1:(length(wss_) - 1)) {
    vel <- (wss_[i] - wss_[i+1]) / max(wss_[i+1], wss_[i])
    if(vel <= threshold) {
      index <- i
      return(index)
    }
  }
}

k <- get_cluster_with_least_change(wss_df$wss, scree_threshold)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous() +
    xlab('Number of clusters')

scree_plot + 
  geom_hline(
      yintercept = wss, 
      linetype = 'dashed'
  )
```

## KMeans Optimization
```{r}
# 8 clusters seems to be the limit for WCSS
km.out <- kmeans(ex_pca, centers = k, nstart = 20)

agg_mean <- aggregate(ex_pca, by=list(cluster=km.out$cluster), mean)
ex_pca <- cbind(ex_pca, cluster=km.out$cluster)
ex_pca <- as.data.frame(ex_pca) %>% relocate(cluster)
```

## Bootstrapping
```{r}
library(fpc)
km.boot <- clusterboot(ex_pca[, -c(1,2,3)], B=1000, bootmethod = "boot", clustermethod=kmeansCBI, krange=k, seed=123)
ex_boot <- ex_pca[,-1]
ex_boot <- cbind(ex_boot, cluster=km.boot$result$partition)
ex_boot <- as.data.frame(ex_boot) %>% relocate(cluster)

# Initialize total within sum of squares error: wss
wss <- numeric(k)

# Look over 1 to n possible clusters
for (i in 1:k) {
  # Save the within cluster sum of squares
  wss[i] <- km.boot$result$resul$withinss[i]
}

# Produce a scree plot
wss_df <- tibble(clusters = 1:k, wss = wss)
k <- get_cluster_with_least_change(wss_df$wss, scree_threshold)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous() +
    xlab('Number of clusters')

scree_plot + 
  geom_hline(
      yintercept = wss, 
      linetype = 'dashed'
  )
```
